The limits of self commitment and private paternalism \thanks{}

### 2022-08-10 donde.tex
consolidate multiple loans and first visit as outcomes

\todo[inline]{Issac: At different points in the paper we use different conventions for whether a positive treatment effect is ``good'' or ``bad.'' We should pick one and stick with it throught to avoid confusion. (E.g. ToT/TuT tables treat positive as good but figure 15 treats negative as good.)}

\todo[inline]{Think more carefully about the ``mistake'' wording here. There's a difference between an ex-ante mistake and an ex-post mistake. Need to think more carefully about this. This also relates to the question about what information to use in the first machine learning exercise. I think if we use the $\text{ATE}(X)$ that's closer to an ex ante measure than if we use, say, $\mathbm{E}[Y_1|X] - Y_0$.}

@@

>>>>

\todo[inline]{Issac: At different points in the paper we use different conventions for whether a positive treatment effect is ``good'' or ``bad.'' We should pick one and stick with it through to avoid confusion. (E.g. ToT/TuT tables treat positive as good but figure 15 treats negative as good.)}

\todo[inline]{Think more carefully about the ``mistake'' wording here. There's a difference between an ex-ante mistake and an ex-post mistake. Need to think more carefully about this. This also relates to the question about what information to use in the first machine learning exercise. I think if we use the $\text{ATE}(X)$ that's closer to an ex ante measure than if we use, say, $\mathbbm{E}[Y_1|X] - Y_0$.}

@@

\begin{figure}[H]
    \caption{Choice of contracts and treatment effects (ToT \& TuT)}
    \label{choose_wrong}
    \begin{center}
        \begin{subfigure}{0.45\textwidth}
        \caption{Mistakes in choice arm}
        \centering
        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}

    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{Financial value of mistake}
        \centering
        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_tot_tut.pdf}
